### 2024-07-25 paper.tex
start on other sl2-tripel

\subsection{Finding an \(\spl_2\)-triple in a simple case}
\par Let
\[e = \begin{pNiceArray}{ccccc}
 0 \\
    1 & 0 \\
  & 1 & \ddots \\
   & & \ddots & 0 \\
   &   &  & 1 & 0
   \end{pNiceArray} \in \mathfrak{sl}_{n},\]
where there are \(n - 1\) ones.
We will find the Slodowy slice at \(e\).
\par As a first step, we will find an \(\spl_2\)-triple with \(e\) as its first element.
Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
From the first equation we find that
\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
\[\sum_i h_{ii} = 0.\]
This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
So we have determined \(h\); it is 
\[h = \begin{pmatrix}
    n - 1  & \\
    & n - 3 \\
    & & \ddots \\
    & & & 3 - n \\
    & & & & 1 - n 
\end{pmatrix}.\]
Now, we can use our expression for \(f\) in terms of \(h\) to obtain
\[f = \begin{pmatrix}
    0 & 1 - n \\
    & 0 & (1 - n) + (3 - n) \\
    & & \ddots & \ddots \\
    & & & 0 & (1 - n) + \cdots + (n - 1) \\
    & & & & 0
\end{pmatrix} = \]
\[\begin{pmatrix}
    0 & 1 (1 - n) \\
      & 0 & 2 (2 - n) \\
    & & 0 & (n - 2) (-2) \\
    & & & 0 & (n - 1) (-1)\\
    & &  & & 0
\end{pmatrix}.\]

\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
Now, suppose \(e = \)

>>>>

\subsection{Finding an \(\spl_2\)-triple in a simple case}
\par Let
\[e = \begin{pNiceArray}{ccccc}
 0 \\
    1 & 0 \\
  & 1 & \ddots \\
   & & \ddots & 0 \\
   &   &  & 1 & 0
   \end{pNiceArray} \in \mathfrak{sl}_{n},\]
where there are \(n - 1\) ones.
We will find the Slodowy slice at \(e\).
\par As a first step, we will find an \(\spl_2\)-triple with \(e\) as its first element.
Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
From the first equation we find that
\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
\[\sum_i h_{ii} = 0.\]
Oops, I didn't actually need to prove that, since \(h \in \spl_n\)... it's nice to know that it's the unique solution in \(\gl_n\) though?
This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
So we have determined \(h\); it is 
\[h = \begin{pmatrix}
    n - 1  & \\
    & n - 3 \\
    & & \ddots \\
    & & & 3 - n \\
    & & & & 1 - n 
\end{pmatrix}.\]
Now, we can use our expression for \(f\) in terms of \(h\) to obtain
\[f = \begin{pmatrix}
    0 & 1 - n \\
    & 0 & (1 - n) + (3 - n) \\
    & & \ddots & \ddots \\
    & & & 0 & (1 - n) + \cdots + (n - 1) \\
    & & & & 0
\end{pmatrix} = \]
\[\begin{pmatrix}
    0 & 1 (1 - n) \\
      & 0 & 2 (2 - n) \\
    & & 0 & (n - 2) (-2) \\
    & & & 0 & (n - 1) (-1)\\
    & &  & & 0
\end{pmatrix}.\]

\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
Now, let 
\[E = \begin{pmatrix}
    0 & 0 \\
    0 & e
\end{pmatrix} \in \spl_{m + n},\]
with \(e\) as in the previous subsection.
We will find \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
Writing \(F = \begin{pmatrix}
    F_{11} & F_{12} \\
    F_{21} & f
\end{pmatrix}\), and similarly for \(H\), we have
\[2E = [H, E] = \begin{pmatrix}
    0 & H_{12}e \\
    0 & he
\end{pmatrix} - \begin{pmatrix}
    0 & 0 \\
    e H_{21} & eh
\end{pmatrix},\]
\[H = [E, F] = \begin{pmatrix}
    0 & 0 \\
    e F_{21} & ef
\end{pmatrix} - \begin{pmatrix}
    0 & F_{12}e \\
    0 & fe
\end{pmatrix}.\]
From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in the previous subsection.
We also see that \(H_{11} = 0\).
Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
Similarly for \(F_{12}\) and \(F_{21}\).
Then our final constraint is that 
\[-2F = [H, F] = \]
\[\begin{pmatrix}
    H_{12} F_{21} & H_{12} F_{22} \\
    H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
\end{pmatrix} - \begin{pmatrix}
    F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
    F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
\end{pmatrix}.\]
Now \(H_{12} F_{21} = F_{12} H_{21} = 0\), by our facts about them from further above.
By the equation above then, we also get \(F_{11} = 0\).
So, the equation above simplifies to 
\[-2F = \begin{pmatrix}
    0 & H_{12} f \\
    h F_{21} & H_{21} F_{12}
\end{pmatrix} - \begin{pmatrix}
    0 & F_{12} h \\
    f H_{21} & F_{21} H_{12}
\end{pmatrix}.\]
